Notes on Design and Implementation of Anglican

### 2015-07-19 paper/paper.tex
better english

Anglican is intended to co-exist with Clojure and be a part of
the source of a Clojure program. To facilitate this, Anglican
programs, or queries, are wrapped by macros (defined in the
\texttt{anglican.emit} namespace), which call the CPS
transformations and define Clojure objects suitable for passing
as arguments to inference algorithms (\texttt{defquery},
\texttt{query}). In addition to defining entire queries,
Anglican promotes modularization of inference algorithm through
definition of \textit{probabilistic functions} using
\texttt{defm} and \texttt{fm} (Anglican counterparts of Clojure
\texttt{defn} and \texttt{fn}), which are written in Anglican,
may include probabilistic forms \texttt{sample} and
\texttt{observe} (as well \texttt{predict} for the output), and
can be seamlessly called from inside Anglican queries, just like
functions locally defined within the same query.

>>>>

Anglican is intended to co-exist with Clojure and be a part of
the source of a Clojure program. To facilitate this, Anglican
programs, or queries, are wrapped by macros (defined in the
\texttt{anglican.emit} namespace), which call the CPS
transformations and define Clojure objects suitable for passing
as arguments to inference algorithms (\texttt{defquery},
\texttt{query}). In addition to defining entire queries,
Anglican promotes modularization of inference algorithms through
definition of \textit{probabilistic functions} using
\texttt{defm} and \texttt{fm} (Anglican counterparts of Clojure
\texttt{defn} and \texttt{fn}), which are written in Anglican,
may include probabilistic forms \texttt{sample} and
\texttt{observe} (as well \texttt{predict} for the output), and
can be seamlessly called from inside Anglican queries, just like
functions locally defined within the same query.
